Experiment

### 2017-05-29 experiment.Rmd
Determine payment

Participants were recruited through [Amazon Mechanical Turk](https://www.mturk.com/mturk/welcome) and were paid $X for their response.

>>>>

Participants were recruited through [Amazon Mechanical Turk](https://www.mturk.com/mturk/welcome) and were paid \$0.75 for their response, which is equivalent to a \$9/hour wage:

```{r calculate-payment}
hourly.wage <- 9
survey.length.minutes <- 5

payment <- survey.length.minutes * (hourly.wage / 60)
payment
```
